---
title: "Class09"
author: "Daniel Chen"
date: "February 7, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Save your input data file to a new 'data' directory
fna.data <- "WisconsinCancer (2).csv"

# Complete the following code to input the data and store as wisc.df
wisc.df <- read.csv(fna.data)
wisc.data <- as.matrix(wisc.df[ ,3:32])

```
```{r}
#set row names
row.names(wisc.data) <- wisc.df$id
```
```{r}
diagnosis <- as.numeric( wisc.df$diagnosis =="M")
```



```{r}
#lets double check
cbind(diagnosis, wisc.df$diagnosis == "M")
```

```{r}
#Q1 how many observations #Q2 want to know how many variables/features in the data are suffixed with  "_mean"?
nrow(wisc.data)
inds <- grep("_mean", colnames(wisc.data))
length(inds)

```

```{r}
#Q3. How many of the observations have a malignant diagnosis?
sum(diagnosis)
```
```{r}
# Check column means and standard deviations
colMeans(wisc.data)

apply(wisc.data,2,sd)
```

```{r}
#perform PCA on wisc.data by completing the following code
wisc.pr <- prcomp(wisc.data, scale=TRUE)
summary(wisc.pr)
```
```{r}
biplot(wisc.pr)
```
```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,2], col= diagnosis+1, xlab= "PC1", ylab= "PC2")
```
```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,3], col= diagnosis+1, xlab= "PC1", ylab= "PC3")

```
##Variance captured in each PC

This info is in the $sdev component of our PCA result
```{r}
variance<- wisc.pr$sdev^2
pve <- round((variance/sum(variance)) * 100, 1)
```

```{r}
plot(pve, xlab = "Principal Component", 
     ylab = "Proportion of Variance Explained", 
     ylim = c(0, 1), type = "o")
```
```{r}
barplot(pve, ylab = "Precent of Variance Explained",
     names.arg=paste0("PC",1:length(pve)), las=2, axes = FALSE)
axis(2, at=pve, labels=round(pve,2) )
```

```{r}
data.scaled <- scale(wisc.data)
round( apply(wisc.data, 2, sd), 1)
```
```{r}
#calculate euclidean distances 
data.dist <- dist(data.scaled)
```
Hierarchical Cluster
```{r}
#hclust(dist(x), method=?)
wisc.hclus <- hclust(data.dist, method = "complete")
plot(wisc.hclus)
```

###Cluster in PCA space

For clustering we need:
1. Distance matrix
2. Clustering function
3. Cutree

Our PCA result of PC1 vs. PC2
```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,2], col= diagnosis+1)

```
```{r}
pc.dist <- dist(wisc.pr$x[,1:2])
pc.hclust <- hclust(pc.dist, method="ward.D2")
plot(pc.hclust)

```

```{r}
#cutree
 grps3 <- cutree(pc.hclust, k=3)
table(grps3)
```

```{r}
type=table(grps3, diagnosis)
# 0=benign, 1=malignant

type
```


```{r}
#making a function to read out "benign" and "malignant" 
for (x in 1:nrow(type)){
  z=type[x,1]
  o=type[x,2]
  print(paste(x,z,o), header= "malignant")
}
```


```{r}
table(grps3, wisc.pr$diagnosis)

```

# 7. Prediction

We will use the `predict()` function that will take our PCA model from before and [new cancer cell data](https://tinyurl.com/new-samples-CSV) and project that data onto our PCA space.

```{r}
#url <- "new_samples.csv"
url <- "https://tinyurl.com/new-samples-CSV"
new <- read.csv(url)
npc <- predict(wisc.pr, newdata=new)
npc

plot(wisc.pr$x[,1:2], col=grps3)
points(npc[,1], npc[,2], col="blue", cex=3, pch=12)

```
