<<<<<<< HEAD
---
title: "Class14: Genome Informatics 1 "
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Asthma SNPs in MXL population

Read file from Ensemble: 

http://uswest.ensembl.org/Homo_sapiens/Variation/Sample?db=core;r=17:39894595-39895595;v=rs8067378;vdb=variation;vf=362656008#373531_tablePanel

```{r}
mxl <- read.csv("373531-SampleGenotypes-Homo_sapiens_Variation_Sample_rs8067378.csv")

head(mxl)

table(mxl$Genotype..forward.strand.)
#sum(mxl$Genotype..forward.strand.== "G|G") would give you counts of how many G|G there are

#percent of G|G? 

table(mxl$Genotype..forward.strand.)/ nrow(mxl)

```

##RNA-seq

fastq qyality scores
Q. Does the first sequence have good quality?

```{r}
q <- "DDDDCDEDCDDDDBBDDDCC@"
library(seqinr)
library(gtools)

asc(s2c(q)) - 33

```

## Population Scale analysis

Does the genotype for rs8067378 influence expression of the important asthma linked genes we found?

```{r}
geno <- read.table("rs8067378_ENSG00000172057.6.txt")
head(geno)
```
```{r}
#how many G|G?

table(geno$geno)

```


```{r}
inds <- geno$geno == "G/G"
summary(geno$exp[inds])
```


```{r}
inds.aa <-  geno$geno == "A/A"
summary(geno$exp[inds.aa])
```

```{r}
inds.ag <-  geno$geno == "A/G"
summary(geno$exp[inds.ag])
```

```{r}
p <- boxplot(exp~geno, data= geno, xlab="rs8067378 genotype", ylab="ENSG00000172057.4 (RPKM)")
```


=======
---
title: "Class14: Genome Informatics 1 "
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Asthma SNPs in MXL population

Read file from Ensemble: 

http://uswest.ensembl.org/Homo_sapiens/Variation/Sample?db=core;r=17:39894595-39895595;v=rs8067378;vdb=variation;vf=362656008#373531_tablePanel

```{r}
mxl <- read.csv("373531-SampleGenotypes-Homo_sapiens_Variation_Sample_rs8067378.csv")

head(mxl)

table(mxl$Genotype..forward.strand.)
#sum(mxl$Genotype..forward.strand.== "G|G") would give you counts of how many G|G there are

#percent of G|G? 

table(mxl$Genotype..forward.strand.)/ nrow(mxl)

```

##RNA-seq

fastq qyality scores
Q. Does the first sequence have good quality?

```{r}
q <- "DDDDCDEDCDDDDBBDDDCC@"
library(seqinr)
library(gtools)

asc(s2c(q)) - 33

```

## Population Scale analysis

Does the genotype for rs8067378 influence expression of the important asthma linked genes we found?

```{r}
geno <- read.table("rs8067378_ENSG00000172057.6.txt")
head(geno)
```
```{r}
#how many G|G?

table(geno$geno)

```


```{r}
inds <- geno$geno == "G/G"
summary(geno$exp[inds])
```


```{r}
inds.aa <-  geno$geno == "A/A"
summary(geno$exp[inds.aa])
```

```{r}
inds.ag <-  geno$geno == "A/G"
summary(geno$exp[inds.ag])
```

```{r}
p <- boxplot(exp~geno, data= geno, xlab="rs8067378 genotype", ylab="ENSG00000172057.4 (RPKM)")
```


>>>>>>> 89ef1019e68c7d6fa279e87dcff261b4c376e2c4
