<<<<<<< HEAD
---
title: "Class13_work"
author: "Daniel Chen"
date: "February 19, 2019"
output: git_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prepare HIV-protease molecule for docking 

First get a PDB sturcture from the online database then clean it up for docking

```{r}
library(bio3d)

file.name <- get.pdb("1hsg")

hiv <- read.pdb(file.name)
```

Read file into R and clean it up (remove non-protein bits) and also we will save the ligand into a separate file

```{r}
hiv

prot <- trim.pdb(hiv, "protein")
lig <- trim.pdb(hiv, "ligand")


write.pdb(prot, file= "1hsg_protein.pdb")
write.pdb(lig, file= "1hsg_ligand.pdb")
```

##Read in autodoc results

```{r}
library(bio3d)
res <- read.pdb("all.pdbqt", multi=TRUE)
write.pdb(res, "results.pdb")
```

```{r}
ori <- read.pdb("1hsg_ligand.pdbqt")
rmsd(ori, res)
```

```{r}
pdb <-read.pdb("1HEL")


m<- nma(pdb)

plot(m)
```

```{r}
mktrj(m, mode=7, file="nma_7.pdb")
```



=======
---
title: "Class13_work"
author: "Daniel Chen"
date: "February 19, 2019"
output: git_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prepare HIV-protease molecule for docking 

First get a PDB sturcture from the online database then clean it up for docking

```{r}
library(bio3d)

file.name <- get.pdb("1hsg")

hiv <- read.pdb(file.name)
```

Read file into R and clean it up (remove non-protein bits) and also we will save the ligand into a separate file

```{r}
hiv

prot <- trim.pdb(hiv, "protein")
lig <- trim.pdb(hiv, "ligand")


write.pdb(prot, file= "1hsg_protein.pdb")
write.pdb(lig, file= "1hsg_ligand.pdb")
```

##Read in autodoc results

```{r}
library(bio3d)
res <- read.pdb("all.pdbqt", multi=TRUE)
write.pdb(res, "results.pdb")
```

```{r}
ori <- read.pdb("1hsg_ligand.pdbqt")
rmsd(ori, res)
```

```{r}
pdb <-read.pdb("1HEL")


m<- nma(pdb)

plot(m)
```

```{r}
mktrj(m, mode=7, file="nma_7.pdb")
```



>>>>>>> 89ef1019e68c7d6fa279e87dcff261b4c376e2c4
